---
title: "Documentation on Shiny app"
author: "Gregor Matheis"
date: "March 11, 2018"
output:
  ioslides_presentation:
    widescreen: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

The shiny application can be found under the link <https://gregormatheis.shinyapps.io/Data-products-week-4-shiny/>

It's hosted on Shiny.IO 

This document is going to show you:

1. Data source
2. Used packages
3. Example plot and list of inputs

## 1. Data source

- Used dataset is from the r datasets pack
- Used data are the swiss data
- Data can be loaded as following

```{r}
datasets::swiss
```

## 2. Used packages

Packages that are used:

- Shiny
- Tidyverse
- Data.table
- Datasets

```{r ,warning=FALSE,  include=FALSE}
require(Shiny)
require(tidyverse)
require(data.table)
require(datasets)
```
Data prep:

```{r}
df<-datasets::swiss
County<-rownames(df)
df$County<-County
setDT(df)
df<-df[County %in% County[1:5]]
```

## 3. Example plot

```{r warning=F}
            ggplot(df)+
                  geom_bar(aes(x=County,y=Education), stat = "identity")+
                  theme_bw()
```

## Thank you

Have fun trying some countys :)
